Modal Abstractions for Virtualizing Memory Addresses

### 2024-07-10 examples.tex
+

Within \textsf{get\_next\_table}, first, we check if the entry whose address is passed as a parameter ($\textsf{entry}$) is present or not (Line 21 in Figure \ref{fig:callptetoinitialize}). To be able to do so, it needs to load the entry value (a 64-bit word divided into bit-fields for corresponding fileds shown in Section {}), and then,check if \textit{presence} bit of the entry is set or not. We see in Specification Line 6 that \textsf{entry} has \textsf{pte-pointsto} that is constructed on the client of \textsf{pte\_get\_next\_table} -- e.g.\textsf{pte\_walkpgdir} in Figure \ref{walkpgdir}.

>>>>

Within \textsf{get\_next\_table}, first, we check if the entry whose address is passed as a parameter ($\textsf{entry}$) is present or not (Line 21 in Figure \ref{fig:callptetoinitialize}). To be able to do so, it needs to load the entry value (a 64-bit word divided into bit-fields for corresponding fileds shown in Section {}), and then,check if \textit{presence} bit of the entry is set or not. In the very first precondition on the client side -- e.g.\textsf{pte\_walkpgdir} in Figure \ref{walkpgdir} -- , we see that \textsf{vpte-ptsto} for the entry being accessed (\textsf{entry}) is constructed -- in Specification Line 6 that \textsf{entry}. Intuitively speaking, we start traversal from a certain entry address at the current level for which we know ($\textsf{entry} \mapsto_{\textsf{id}} \textsf{\_}$ in Line 3 in Figure \ref{walkpgdir}) that there is a memory mapping ($\textsf{entry+KERNBASE} \mapsto_{\textsf{vpte,qfrac}} \textsf{entry entry\_val}$  Line 15 in Figure \ref{walkpgdir}) that can be used to explore deeper in the page-tree.
